Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-17 paper.qmd
Updated Figure12

proj_obj1 <- get_projection(projection = projection,
                            proj_scale = 1,
                            scaled_data = scaled_c_shaped_data,
                            scaled_data_model = scaled_c_shaped_data_model,
                            distance_df_small_edges = distance_df_small_edges_c_shaped_structure,
                            axis_param = list(limits = 0.35,
                                              axis_scaled = 2,
                                              axis_pos_x = -0.28,
                                              axis_pos_y = -0.28,
                                              threshold = 0.017))

@@

five_c_shaped_proj_tsne_model1 <- plot_proj(
    proj_obj = proj_obj1,
    point_param = c(1.5, 0.5), # size, alpha, color
    line_param = c(0.8, 0.4, "#000000"), # linewidth, alpha
    plot_limits = c(-0.35, 0.35), 
    title = "a3", 
    cex = 2,
    position = c(0.08, 0.9),
    axis_text_size = 4, 
    is_color = TRUE) +
    scale_color_manual(values = c('#d9d9d9', '#800026')) +
    theme(aspect.ratio = 1,
          legend.position = "none")

@@

five_c_shaped_proj_tsne_model1_selected <- plot_proj(
    proj_obj = proj_obj1, 
    point_param = c(1.5, 0.5), # size, alpha, color
    line_param = c(0.8, 0.4, "#000000"), # linewidth, alpha
    plot_limits = c(-0.35, 0.35), 
    title = "b3", 
    cex = 2,
    position = c(0.08, 0.9),
    axis_text_size = 4, 
    is_color = TRUE) +
    scale_color_manual(values = c('#d9d9d9', '#800026')) +
    theme(aspect.ratio = 1,
          legend.position = "none")
```

>>>>

proj_obj1 <- get_projection(projection = projection,
                            proj_scale = 1,
                            scaled_data = scaled_c_shaped_data,
                            scaled_data_model = scaled_c_shaped_data_model,
                            distance_df_small_edges = distance_df_small_edges_c_shaped_structure,
                            axis_param = list(limits = 0.4,
                                              axis_scaled = 3,
                                              axis_pos_x = -0.28,
                                              axis_pos_y = -0.28,
                                              threshold = 0.02))

@@

five_c_shaped_proj_tsne_model1 <- plot_proj(
    proj_obj = proj_obj1,
    point_param = c(1.5, 0.5), # size, alpha, color
    line_param = c(0.8, 0.4, "#000000"), # linewidth, alpha
    plot_limits = c(-0.35, 0.35), 
    title = "a3", 
    cex = 2,
    position = c(0.08, 0.9),
    axis_text_size = 4.5, 
    is_color = TRUE) +
    scale_color_manual(values = c('#d9d9d9', '#800026')) +
    theme(aspect.ratio = 1,
          legend.position = "none")

@@

five_c_shaped_proj_tsne_model1_selected <- plot_proj(
    proj_obj = proj_obj1, 
    point_param = c(1.5, 0.5), # size, alpha, color
    line_param = c(0.8, 0.4, "#000000"), # linewidth, alpha
    plot_limits = c(-0.35, 0.35), 
    title = "b3", 
    cex = 2,
    position = c(0.08, 0.9),
    axis_text_size = 4.5, 
    is_color = TRUE) +
    scale_color_manual(values = c('#d9d9d9', '#800026')) +
    theme(aspect.ratio = 1,
          legend.position = "none")
```
